\sysfull

### 2018-04-16 paper/evaluation.tex
revision of evaluation up to section 9.2

Our results illustrate key findings about \sys. We show through extensive qualitative and quantitative evaluation that (i) \sys \emph{provides computation progress} at the partial task level, guaranteeing execution at the worst intermittent energy conditions where state-of-the-art runtimes fail; (ii) usually \emph{improves execution speed} of applications compared to state-of-the-art runtimes; (iii) \sys, through coalescing mechanism, \emph{reduces the memory protection overhead} significantly; and (iv) that \sys is \emph{more generic to use} and allows to interact with code written for non-intermittent devices more easily.

@@

\indent \textbf{Coalescing Algorithms Efficiency.} We have measured the time spent on executing (i) useful task code, (ii) wasted task code (that have to be re-executed due to uncommitted progress), and (iii) commits for all coalescing strategies (EB, EA and ETA) and all benchmarks. We compared our results to non-coalescing \sys (NC). The experiment was performed at 15\,cm WISP-to-exciter distance and normalized per benchmark. All benchmarks were using 256-B pages, except for \textbf{bc} which was using 32-B pages. Those page sizes are the ones yielding the best performance, selected among the set mentioned in Section~\ref{sec:implementation}. Detailed investigation of \sys's paging performance will be given in Section~\ref{sec:results_memory_management}.
%
The result is presented in Figure~\ref{fig:overallOverheadBreakdown}. We clearly see that all coalescing strategies make a better use of the resources for \emph{all} benchmarks (except for EB in \textbf{bc}).
With a more thorough look, one can notice that the re-execution penalty, i.e. the time wasted running tasks whose progress could not be committed due to a power failure, is minimized by NC. This is obvious, since this strategy makes the system commit after each static task.
On the other hand, the burden on committing so frequently reflects in a degraded performance with respect to coalescing, motivating one of the needs raised by this work.
EA and ETA strategies provide the best balance between re-execution penalty and commit cost. For this reason we proceed with the investigation of \sys without considering EB coalescing.

\begin{figure}
	\centering
	\includegraphics[width=0.49\columnwidth]{figures/overallOverhead}
	\includegraphics[width=0.49\columnwidth]{figures/memAccess}
	\caption{Kernel overhead. Left: high-level load distribution; right: detailed breakdown of memory accesses overhead from the left figure). NC: no coalescing, EA: energy-aware coalescing, ETA: energy- and task-aware coalescing. \todo{rename legend entry 'task code' to 'user code'; rename y-axis to 'Load (\%)'}{Amjad}}
	\label{fig:coalEfficiency}
\end{figure}

\textbf{Kernel Overhead Breakdown.} We now proceed with investigating how much utilization \sys's kernel steals to user code, quantifying task transitions and memory accesses overhead. For a broader picture, we profile kernel load for NC as well. The result for all benchmarks are measured in the same way as for the results presented above (i.e. given in Figure~\ref{fig:overallOverheadBreakdown}) and using the same page sizes as in the previous experiment. The outcome is presented in Figure~\ref{fig:coalEfficiency} (left side).
%
As expected, non-coalescing (NC) \sys introduces a huge cost of task transitions and commits (which recapitulates the result presented in Figure~\ref{fig:overallOverheadBreakdown}). For both coalescing strategies (EA and ETA) protected variables' accesses constitutes about 30\% of the whole load across all benchmarks. In fact, dynamic address translation is the most critical bottleneck for \sys.

@@

We characterize \sys by studying how its execution time varies due to task adaptation. We look at \sys in isolation and in comparison to Alpaca.

\textbf{\sys versus \sys.} Figure~\ref{fig:coalescing} shows the run time of \sys's three coalescing strategies for all benchmarks normalized to NC's performances. We show data from experiments measured in the same way as for the results in Section~\ref{sec:coala_overhead}.

@@

\textbf{\sys versus non-adaptive Task-based Model.} We now evaluate \sys's run time and compare it to Alpaca, a non-adaptive task-based system. Results are presented in Figure~\ref{fig:runtime}. For each application we measured its execution time using real wireless power provisioned by the RF signal generator at three distances (refer again to Section~\ref{sec:implementation}).
%
The plot presents the average execution time of each application with, for Coala and Alpaca, normalized to the latter. The results show that \sys provides a performance benefit compared to Alpaca for most applications (all except for \textbf{ar} and \textbf{cuckoo} at 30 and 50 cm). The improvement is the greatest for applications that perform repeated write after read operations, particularly if involving arrays (\textbf{dijkstra}, \textbf{fft} and \textbf{sort}). This effect is seen at all distances on intermittent power. In applications with protected variables (or array elements) accessed next to each other, but residing in different SRAM or FRAM pages, \sys incurs overhead from memory virtualization that causes its performance to be comparable to (or worse than) Alpaca (\textbf{ar}, \textbf{cuckoo}).
%
Another critical observation is that \textbf{fft} benchmark did not complete at any distance larger than 0.15\,cm. As we will show now, \sys's task downscaling mechanism, which was intendedly disabled for this experiment, will be able to solve this issue.

@@

\textbf{Task Downscaling Execution Time.} We have enabled task downscaling and measured the execution time for \textbf{fft} benchmark at 60\,cm from the exciter, even farther than the farthest distance at which, without this feature, this benchmark could not run to completion (refer again to Figure~\ref{fig:coalescing} and $\infty$ marks). \sys could execute the benchmark successfully with an average on-time of 201\,ms for NC and of 180\,ms for ETA, respectively 2.16x and 2.31x slower than at 15\,cm, which is not bad compared to the infinite run time of a static system (Alpaca in this case).

>>>>

Our results illustrate key findings about \sys. We show through extensive qualitative and quantitative evaluation that (i) \sys \emph{provides computation progress} at the partial task level, guaranteeing execution at the worst intermittent energy conditions where state-of-the-art runtimes fail; (ii) \sys usually \emph{improves execution speed} of applications compared to state-of-the-art runtimes; (iii) \sys, through coalescing mechanism, \emph{reduces the memory protection overhead} significantly; and  that (iv) \sys is \emph{more generic to use} and allows to interact with code written for non-intermittent devices easily.

@@

\indent \textbf{Coalescing Algorithms Efficiency.} We have measured the time spent on executing (i) useful task code, (ii) wasted task code (that have to be re-executed due to uncommitted progress), and (iii) commits for all coalescing strategies (EB, EA and ETA) and all benchmarks. We compared our results to non-coalescing (NC). The experiment was performed at 15\,cm WISP-to-exciter distance and normalized per benchmark. All benchmarks were using 256\,B pages, except for \textbf{bc} which was using 32\,B pages. Those page sizes are the ones yielding acceptable performance\footnote{Detailed investigation of \sys's paging performance will be given in Section~\ref{sec:results_memory_management}.}, selected among the set mentioned in Section~\ref{sec:implementation}.

The result is presented in Figure~\ref{fig:overallOverheadBreakdown}. We clearly see that all coalescing strategies make a better use of the resources for \emph{all} benchmarks (except for EB in \textbf{bc}).
With a more thorough look, one can notice that the re-execution penalty, i.e. the time wasted running tasks whose progress could not be committed due to a power failure, is minimized by NC. This is obvious, since this strategy makes the system commit after each static task.
On the other hand, the burden on committing so frequently reflects in a degraded performance with respect to coalescing, motivating one of the needs raised by this work.
EA and ETA strategies provide the best balance between re-execution penalty and commit cost. For this reason we proceed with the investigation of \sys without considering EB coalescing.

\begin{figure}
	\centering
	\includegraphics[width=0.49\columnwidth]{figures/overallOverhead}
	\includegraphics[width=0.49\columnwidth]{figures/memAccess}
	\caption{\sys kernel overhead. Left: high-level load distribution; right: detailed breakdown of memory accesses overhead (from the left figure). NC: no coalescing, EA: energy-aware coalescing, ETA: energy- and task-aware coalescing. \todo{rename legend entry 'task code' to 'user code'; rename y-axis to 'Load (\%)'}{Amjad}}
	\label{fig:coalEfficiency}
\end{figure}

\textbf{\sys Kernel Overhead Breakdown.} We now proceed with investigating how much utilization \sys's kernel steals to user code, quantifying task transitions and memory accesses overhead. For a broader picture, we profile kernel load for NC as well. The result for all benchmarks are measured in the same way as for the results presented above (i.e. given in Figure~\ref{fig:overallOverheadBreakdown}) and using the same page sizes as in the previous experiment. The outcome is presented in Figure~\ref{fig:coalEfficiency} (left side).
%
As expected, non-coalescing (NC) \sys introduces a huge cost of task transitions and commits (which recapitulates the result presented in Figure~\ref{fig:overallOverheadBreakdown}). For both coalescing strategies (EA and ETA) protected variables' accesses constitutes about 30\% of the whole load across all benchmarks. In fact, dynamic address translation is the most critical bottleneck for \sys.

@@

We proceed with characterizing \sys by studying how its execution time varies due to task adaptation. We look at \sys in isolation and in comparison to Alpaca.

\textbf{\sys Cross-Evaluation.} Figure~\ref{fig:coalescing} shows the run time of \sys's three coalescing strategies for all benchmarks normalized to NC's performances. We show data from experiments measured in the same way as for the results in Section~\ref{sec:coala_overhead}.

@@

\textbf{\sys versus non-adaptive Task-based Model.} We now evaluate \sys's run time and compare it to Alpaca---a non-adaptive task-based system. Results are presented in Figure~\ref{fig:runtime}. For each application we measured its execution time using real wireless power provisioned by the RF signal generator at three distances (refer again to Section~\ref{sec:implementation}). The plot presents the average execution time of each application for Coala and Alpaca, normalized to the latter. The results show that \sys provides a performance benefit compared to Alpaca for most applications (all except for \textbf{ar} and \textbf{cuckoo} at 30 and 50\,cm). The improvement is the greatest for applications that perform repeated write after read operations, particularly if involving arrays (\textbf{dijkstra}, \textbf{fft} and \textbf{sort}). This effect is seen at all distances on intermittent power. In applications with protected variables (or array elements) accessed next to each other, but residing in different SRAM or FRAM pages, \sys incurs overhead from memory virtualization that causes its performance to be comparable to (or worse than) Alpaca (\textbf{ar}, \textbf{cuckoo}).
%
Another critical observation is that \textbf{fft} benchmark did not complete at any distance larger than 0.15\,cm. As we will show now, \sys's task downscaling mechanism, which was intendedly disabled for this experiment, will be able to solve this issue.

@@

\textbf{Task Downscaling Execution Time.} We have enabled task downscaling and measured the execution time for \textbf{fft} benchmark at 60\,cm from the exciter, that is, even \emph{farther} than the farthest distance at which (without this feature) this benchmark could not run to completion (refer again to Figure~\ref{fig:coalescing} and $\infty$ marks). \sys could execute the benchmark successfully with an average `on' time (the time spent for useful computation excluding energy breaks) of 201\,ms for NC and of 180\,ms for ETA, respectively 2.16$\times$ and 2.31$\times$ slower than at 15\,cm, which is impressive compared to the infinite run time of Alpaca, being a static system.
